### 2014-11-06 summary/AperturePhot1/aperPhotSummary.tex
aperture photometry summary1 finished

\maketitle % Print the title
\section{Summary}
\begin{enumerate}
\item Using cross correlation, images can be aligned with precision of
  $\sim 0.01$ pixels, which is far better than the precision that IDL
  \texttt{cntrd.pro} and \texttt{gcntrd.pro} routines can
  provide. According to the patterns on PSF subtracted images, cross
  correlation has better performance tan WCS alignment.
\item Aperture photometry for secondary object in ABPIC system is
  carried out with a fixed aperture radius of 5 pixels. The light
  curves are very similar to Glenn's measurement. The light curves for
  two filters, F125W and F160W have better agreement in my
  measurement.
\item Taking only statistical uncertainty (counting error) and
  background fluctuations into account, a rough estimation gives an
  relative uncertainty of 0.3\% for one photometry measurement.

\end{enumerate}
\section{Image Registration}
\subsection{Image Registration Precision Test}
The performance of image registration method is valuated by the accuracy of
the measurement for shift between two images. In practice, I
choose one image, shift this image with a specific distance with
\texttt{fshift.pro}, measure the shift, and calculate the offset of
the measured shift and real shift. With above procedure, I tested the
performance of 3 image registration method. Results are plotted in figure \ref{fig:shift1}.\par

The offsets for cntrd and gcntrd methods can be as large as 0.2 - 0.3
pixels. However cross correlation method can limit the offset within
0.06 pixels. It is surprising that none of the three distributions of
offsets has a Gaussian like  profile. For cross correlation, I plotted
the offset against the real shift distance. It turned out that the
offset oscillates with shift distance with a period of exact 1 pixel
and an amplitude of 0.05 pixels. I do not know clearly why they have
such a relationship.\par

According to the test result, cross correlation has a much better
performance on registration images.

@@

\subsection{Modification of  Cross correlation}
The general idea of cross correlation method is that it calculate
cross correlation matrix of one image and one reference image. The
coordinate of the maximum in cross correlation matrix then can be
converted to the shifts in x and y direction of the image  relative to
the reference image. To locate the peak in cross correlation matrix
is one key factor of the accuracy of this method. The original
\texttt{crosscorr.pro} routine use \texttt{polyfit2d.pro} to find the
maximum, which uses a polynomial function (default order is 4) to fit
the an area around the maximum value (default is a (5 pixel)$^{2}$
square) and find the peak. I tried to fit either with a higher order
or larger area, the result turned to be unstable. Especially, when I
kept on using an order of 4 polynomial function to fit a (10
pixel)$^{2}$ square around the peak, the program got stuck and
returned error.\par

Therefore, I tried \texttt{mpfit2dpeak.pro} routine which fits either
Gaussian, Lorentz or Moffat function to find the peak. It turned out
that  mpfit could improve the accuracy of cross correlation for
nearly an order of magnitude. With mpfit, the offset for measured
shift and real shift can be limited within 0.008 pixels. However, the
weird oscillation still exists.\par

@@

\subsection{Test with Noise Adding in}
Primary star image is subtracted with a PSF image that has a different
rolling angle. Thus it is important to know the accuracy in the
scenario  where only the primary star image stays the same, other
objects rolled to a specific angle. To simulate rolling, I add 5 fake
star images in random positions to both original image and shifted
image and then use cross correlation to measure the shift. As shown in
figure \ref{fig:shift2}, noise star images does not affect the
accuracy too much.

\begin{figure}[h]
      \centering
      \includegraphics[width=0.8\textwidth]{crosscorr_cenWithNoise}
      \caption{offset for measured shift and real shift. Original
        image and shifted iamge were both added with 5 fake star in
        random poistions.}
      \label{fig:shift2}
    \end{figure}

@@

For one specific image(img$_{0}$), every other image(img$_{i}$) that was taken with the same
filter and different rolling angle were selected to be
subtracted. With equation \ref{eqn:fit}:
\begin{equation}
  \label{eqn:fit}
  res = \sum(img_{0} - c\cdot img_{i})^{2}
\end{equation}
tunable scale factor $c$ is calculated with minimum least square
fitting. The PSF is chosen with the criterion of least residual. \par

Figure \ref{fig:subcomp} illustrate the difference of PSF subtraction
results between cross correlation and WCS registration. It is clearly
shown that cross correlation gives a better alignment that the
residual image is much more even. WCS aligned PSF is clearly offset to
downright direction.\par

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{cc_example}
  \includegraphics[width=\textwidth]{wcs_example}
  \caption{PSF subtraction comparison. Above: cross
    correlation. Below: WCS}\label{fig:subcomp}
\end{figure}
\section{Aperture Photometry Result}
\subsection{Light Curves}

The light curve measurements for both absolute fluxes and relative
fluxes are shown in Figure \ref{fig:lightcurve}. Figure
\ref{fig:glenn} is Glenn's preliminary measurements. The lower plot in
figure \ref{fig:lightcurve} is very similar to figure
\ref{fig:glenn}. However, in figure \ref{fig:glenn}, the light curves
for F125W and F160W show considerable discrepancies in 5th and 6th
orbits. However in my measurement, the two curves agree better. Apart
from this, the most prominent features are shown in both light
curves, e.g. the light curves are lower in 2nd orbit and the
discrepancy at start of the 3rd orbit.

>>>>

\maketitle % Print the title
\section{Summary}
\begin{enumerate}
\item Using cross correlation, images can be aligned with precision of
  $\sim 0.01$ pixels, which is far better than the precision that IDL
  \texttt{cntrd.pro} and \texttt{gcntrd.pro} routines can
  provide. According to the patterns on PSF subtracted images, cross
  correlation has better performance than WCS alignment.
\item Aperture photometry for secondary object in ABPIC system is
  carried out, with a fixed aperture radius of 5 pixels. The light
  curves are very similar to Glenn's measurement. The light curves for
  two filters, F125W and F160W seem to have better agreement in my
  measurement.
\item Taking only statistical uncertainty (counting error) and
  background fluctuations into account, a rough estimation gives an
  relative uncertainty of 0.3\% for one photometry measurement.

\end{enumerate}
\section{Image Registration}
\subsection{Image Registration Precision Test}
The performance of image registration method is valuated by the
accuracy of the measurement for shift between two images. In practice,
I choose one image, shift it for a specific distance with
\texttt{fshift.pro}, measure the shift with various methods, and
calculate the difference of the measured shift and real shift. With
above procedure, I tested the performances of 3 image registration
methods. Results are demonstrated in figure \ref{fig:shift1}.\par

The difference of measured shift and real shift  for cntrd and gcntrd methods can be as large as 0.2 - 0.3
pixels. In contrast, cross correlation method can limit the offset within
0.06 pixels. It is surprising that none of the three distributions of
offsets has a Gaussian shaped  profile. For cross correlation, I plotted
the offset against the real shift distance. It turned out that the
offset oscillates with shift distance with a period of exact 1 pixel
and an amplitude of $\sim$0.06 pixels. I do not know clearly why they have
such a relationship.\par

Nevertheless, according to the test result, cross correlation has a better
performance on registration images.\par

@@

\subsection{Modification of  Cross correlation}
The general idea of cross correlation registration is to use the
position of peak  in cross correlation matrix calculated with
two images to determine how they shift from each other.  To locate the
peak in cross correlation matrix is one key factor of the accuracy of
this method. The original \texttt{crosscorr.pro} routine uses
\texttt{polyfit2d.pro} to find the maximum, which fits a polynomial
function (default order is 4) to an area around the maximum
value (default is a (5 pixel)$^{2}$ square) and find the peak. I tried
to fit either with a higher order or larger area, but the result turned to
be unstable. Especially, when I kept on using an order of 4 polynomial
function to fit a (10 pixel)$^{2}$ square around the peak, the program
got stuck and returned error.\par

Therefore, I tried \texttt{mpfit2dpeak.pro} routine which fits either
Gaussian, Lorentz or Moffat profile  to find the peak. It turned out
that  mpfit could improve the accuracy of cross correlation for
nearly an order of magnitude. With mpfit, the offset for measured
shift and real shift can be limited within 0.008 pixels. However, the
weird oscillation still exists.\par

@@

\subsection{Test with Noise Adding in}
Primary star image is subtracted with a PSF image that has a different
rolling angle. Thus it is important to know the accuracy in the
scenario  where only the primary star image stays the same, other
objects rolled to a specific angle. To simulate rolling, I added 5 fake
star images in random positions to both original image and shifted
image and then use cross correlation to measure the shift. As shown in
figure \ref{fig:shift2}, fake star images does not affect the
accuracy too much.

\begin{figure}[h]
      \centering
      \includegraphics[width=0.8\textwidth]{crosscorr_cenWithNoise}
      \caption{offset for measured shift and real shift. Original
        image and shifted iamge were both added with 5 fake star in
        random positions.}
      \label{fig:shift2}
    \end{figure}

@@

For one specific image(img$_{0}$), every other image(img$_{i}$) that was taken with the same
filter and different rolling angle were selected to be
subtracted from img$_{0}$. With equation \ref{eqn:fit}:
\begin{equation}
  \label{eqn:fit}
  res = \sum(img_{0} - c\cdot img_{i})^{2}
\end{equation}
tunable scale factor $c$ is calculated with minimum least square
fitting. The PSF is chosen with the criterion of least residual. \par

Figure \ref{fig:subcomp} illustrate an example of the difference of
PSF subtraction results between cross correlation and WCS
registration. It is clearly shown that cross correlation gives a
better alignment. The residual image is more even with cross
correlation registration. WCS aligned PSF is clearly offset to
downright direction.\par

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{cc_example}
  \includegraphics[width=\textwidth]{wcs_example}
  \caption{PSF subtraction comparison. Above: cross
    correlation. Below: WCS}\label{fig:subcomp}
\end{figure}

\section{Aperture Photometry Result}
\subsection{Light Curves}

The light curve measurements for both absolute fluxes and relative
fluxes are shown in Figure \ref{fig:lightcurve}. Figure
\ref{fig:glenn} is Glenn's preliminary measurements. The lower plot in
figure \ref{fig:lightcurve} is very similar to figure
\ref{fig:glenn}. However, in figure \ref{fig:glenn}, the light curves
for F125W and F160W show considerable discrepancies in 5th and 6th
orbits. In my measurement, the two curves seemed to agree better. Apart
from this, the most prominent features are shown in both light
curves, e.g. the light curves are lower in 2nd orbit and there is a 
discrepancy of two curves at start of the 3rd orbit.
